---
title: "HW1: GitHub and Errors"
author: "kaori hirano"
date: "6 8 2023"
format: pdf
---

## Q1

```{r line-by-line}
??mpg
library(tidyverse)
library(dplyr)
library(ggplot2)
#| error: true
??summarize
mpg %>% filter(class == "subcompact") %>%
  group_by(drv)
  summarize(mpg, median_cty_mpg = median(cty),
            sd_cty_mpg = sd(cty),
            avg_cty_mpg = mean(cty))
```

the pipe function is part of dplyr so we need to load that before using it, so I added that, as well as ggplot2 because it showed up later and tidyverse because I couldn't remember if %>% was part of dplyr or tidyverse (after referencing the documentation it is from dplyr).  

First I looked up summarize because I wasn't familiar with it. I saw you needed a table to draw the information from, which would be mpg, so I added mpg. I put a c() in front of the data, but thought it made more sense based on the wording to have each number be a row column instead of a row. 
## Q2

```{r scatter-plot}
#| error: true

??mpg
mpg %>% 
  ggplot(aes(x = hwy, y = cty)) + 
  geom_point() +
  labs(x = "Highway", ylabel = "City", 
       title = "Miles per Gallon - Highway vs City")
```

Was missing + so I added the + instead of %>% which is what is used for ggplots. 

## Q3

```{r vectors}
#| error: true
vec1 <- c(1, 2, 3)
vec2 <- c(3, -2, 2.305)

Map('*', vec2, vec1)
```

The text was missing the concatenate function so I added that. you can't just have a bunch of numbers strung together without it. 
Then the %* didn't make sense so I added Map which would multiply each element. 
Then I added a 1 to call a variable that was previously defined because you can't randomly reference variables that don't exist. 

## Q4 

```{r avg_avg}
#| error: true
library(matrixStats)
rowMeans2(mpg_fl, rows = c('hwy', 'cty'))
# not really sure whats going on here     
mean(mpg_fl$mean_hwy, mpg_fl$mean_cty)
  
mpg_fl <- mpg %>% 
  group_by(fl) %>% 
  summary(
    mean_hwy, mean_cty = mean(hwy, cty)
  )


```

for the second part I look at the documentation, saw it needed and underscore. then tried to figure out what F1 was doing in the code, then realized it was supposed to be fl so I changed that. 

## Q5 

```{r matrix}
#| error: true
a <- c(1,2,3)
b <- c("a","b","c")
d <- cbind(a,b) # Put them together
as.numeric(d[1]) + 1
```

when the two were combined into d, everything became a string because letters can't be numbers. to do addition you need numbers, so I made the element we needed to add 1 to into a number using as.numeric. 