---
title: "HW1: GitHub and Errors"
author: "Insert your name here"
date: "Insert date here"
format: pdf
---

## Q1

```{r line-by-line}
#| error: true
mpg %>%
  filter(class == "subcompact") %>%
  group_by(drv)
  summarize(median_cty_mpg = median(cty),
            sd_cty_mpg = sd(cty),
            avg_cty_mpg = average(cty))
```

Remove this text, and add your narrative description of the process for
answering Question 1 here.

## Q2

```{r scatter-plot}
#| error: true
mpg %>% 
  ggplot(aes(x = highway, y = cty)) %>% 
  geom_point() +
  labs(x = "Highway", ylabel = "City", 
       title = "Miles per Gallon - Highway vs City")
```

Remove this text, and add your narrative description of the process for
answering Question 2 here.

## Q3

```{r vectors}
#| error: true
vec1 <- c(1, 2, 3)
vec2 <- (3, -2, 2.305)

vec2 %* vec
```

Remove this text, and add your narrative description of the process for
answering Question 3 here.

## Q4 

```{r avg_avg}
#| error: true
mean(mpg_fl$mean_hwy, mpg_fl$mean_cty)

mpg_fl <- mpg %>% 
  groupby(Fl) %>% 
  summary(
    mean_hwy, mean_cty = mean(hwy, cty)
  )
```


Remove this text, and add your narrative description of the process for
answering Question 4 here.

## Q5 

```{r matrix}
#| error: true
a <- c(1,2,3)
b <- c("a","b","c")
d <- cbind(a,b) # Put them together
d[,1] + 1
```


Remove this text, and add your narrative description of the process for
answering Question 5 here.
